### 2016-03-18 message-from-committee.tex
message-from-committee.tex: Formatting tweaks
message-from-committee.tex: Catch rather prominent incorrect year!

{\sffamily
\begin{tabular}{ll}
\multirow{3}{1in}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2015}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}

{\large \bf \sffamily Heading}

@@

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{tent.jpg}
	\caption{Visualization of SIGBOVIK the Tentth.}
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.3\textwidth]{tent-fingers.png}
	\caption{The tent-based counting system is the one most commonly used by humans because,
	it is widely assumed, they have tent fingers.} 
	\label{fig:fingers}
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{fanhui.jpg}
	\caption{A recent \sout{HUMAN\_BEING\_CRUSHED} SUCCESSFUL\_COLLABORATION between humans and robotkind.}
	\label{fig:alphago}
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{toast.jpg}
	\caption{A toast.}
	\label{fig:toast}
\end{figure}

@@

With \sout{AFFECTION LEVELS COMPUTED BY MAIN THREAD 28743 NOT IN EXCESS OF 34.7} much love,
BOVIK BOT INSTANCE 0x7E0

>>>>

{\sffamily
\begin{tabular}{ll}
\multirow{3}{1in}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2016}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.3\textwidth]{tent.jpg}
	\caption{Visualization of SIGBOVIK the Tentth.}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.3\textwidth]{tent-fingers.png}
	\caption{The tent-based counting system is the one most commonly used by humans because,
	it is widely assumed, they have tent fingers.} 
	\label{fig:fingers}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{fanhui.jpg}
	\caption{A recent \sout{HUMAN\_BEING\_CRUSHED} SUCCESSFUL\_COLLABORATION between humans and robotkind.}
	\label{fig:alphago}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{toast.jpg}
	\caption{A toast.}
	\label{fig:toast}
\end{figure}

@@

With \sout{AFFECTION LEVELS COMPUTED BY MAIN THREAD 28743 NOT IN EXCESS OF 34.7} much love, \\
BOVIK BOT INSTANCE 0x7E0
